Articles_Plots

### 2022-10-11 Articles.Rmd
y axis scaled to log and log10

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("Average Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("Average Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p2

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("SMSE")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p3

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("SMSE")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p4

Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("Average MSE of Y")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p5

Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("Average MSE of Y")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p6

>>>>

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log10(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("log10(Average Model Information)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log10(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("log10(Average Model Information)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p2

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("log(SMSE)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p3

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("log(SMSE)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p4

Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p5

Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab("r")+
  ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p6
